\cvsection{Publications: Journals}
\begin{cventries}
	\cventry
	{} % \textbf{Siddiqui MS}ffiliation/role
	{} % Organization/group
	{} % Location
	{} % Date(s)
	{
		\begin{cvitems}
			\item {Tabib M, \textbf{Siddiqui MS}, Fonn E, Rasheed A, Kvamsdal T, “LES and POD to differentiate the wake dynamics simulated by Actuator Line and Sliding
				Mesh Interface techniques for an industrial scale
				wind turbine.”, Journal of Physics Conference Series, pp. 012044, Vol. 854, 2017.}
			\item {\textbf{Siddiqui MS}, Rasheed A, Tabib M, Kvamsdal T, “Influence of Tip Speed Ratio on Wake Flow Characteristics Utilizing Fully Resolved CFD Methodology ”, Journal of Physics Conference Series, pp. 012043, Vol. 854, 2017.}
			\item {\textbf{Siddiqui MS}, Rasheed A, Tabib M, Fonn E, Kvamsdal T, “On the interaction between Wind Farms and Marine Boundary Layer”, Proceedings of the ASME 2017 36th International Conference on Ocean, Offshore and Arctic Engineering}
			\item {\textbf{Siddiqui MS}, Rasheed A, Tabib M, Kvamsdal T, “Quasi-Static \& Dynamic Numerical Modeling of Full Scale NREL 5MW Wind Turbine”, Elsevier Energy Procedia Journal, pp. xxxx, 2017.}
			\item {\textbf{Siddiqui MS}, Rasheed A, Tabib M, Kvamsdal T, “Simulating Single turbine and associated wake development - validation and comparison of computational methods (Actuator Line Vs Sliding Mesh Interface Vs Multiple Reference Frame)”, Elsevier Energy Procedia Journal, pp. xxxx, 2017.}
			\item {Rasheed A, Tabib M, \textbf{Siddiqui MS}, Foon E, Suld JK, Kvamsdal T, “A comprehensive multiscale numerical framework for wind energy modeling”, Elsevier Energy Procedia Journal, pp. xxxx, 2017.}
			\item {Tabib M, Rasheed A, \textbf{Siddiqui MS}, Kvamsdal T, “A full-scale 3D Vs 2.5D Vs 2D analysis of flow
			pattern and forces for an industrial-scale 5MW
			NREL reference wind-turbine.”, Elsevier Energy Procedia Journal, pp. xxxx, 2017.}
			\item {Fonn E, \textbf{Siddiqui MS}, Rasheed A, Tabib M, Kvamsdal T, “A step towards a reduced order modeling of flow characterized by wakes using Proper Orthogonal Decomposition”, Elsevier Energy Procedia Journal, pp. xxxx, 2017.}
			\item{\textbf{Siddiqui MS}, Rasheed A, Tabib M, Kvamsdal T, “Insights on aerodynamics of the industrial-scale NREL 5MW reference wind turbine through comparison of different numerical frameworks with variable levels of geometric approximations ”, Wind Energy, 2016.}
			\item{\textbf{Siddiqui MS}, Rasheed A, Kvamsdal T, Tabib M, “Comparison of 2D and 3D RANS Based Simulations of NACA0015 Offshore Wind Turbine Blade  ”, Elsevier Journal of Applied Energy, 2016.}
			\item{\textbf{Siddiqui MS}, Rasheed A, Tabib M, Kvamsdal T, “Numerical Analysis of NREL 5MW Wind Turbine: A Study Towards a Better Understanding of Wake Characteristic and Torque Generation Mechanism ”, Journal of Physics Conference Series 753(2016)032059.}
			\item {\textbf{Siddiqui MS}, Rasheed A, Kvamsdal T, Tabib M, “Three-Dimensional Variable Turbulent Intensity Flow Field Characterization of a Vertical Axis Wind Turbine”, Elsevier Energy Procedia Journal, pp. 312-320, 2015.}
			\item {Saif M, Rabbani T, Akhtar T, Durrani N, \textbf{Siddiqui MS}, “Reduced-Order Modeling of Torque on a Vertical-Axis Wind Turbine at Varying Tip-Speed Ratios”, Journal of Computational and Nonlinear Dynamics, American Society of Mechanical Engineers, Volume 10, pp. 041012, 2015.}
			\item {\textbf{Siddiqui MS}, Durrani N, Akhtar I, “ Quantification of the Effects of Geometric Approximations on the Performance of a Vertical Axis Wind Turbine: A Numerical Approach”, Elsevier Renewable Energy Journal, Volume 74, pp. 661-670, 2015.}
		\end{cvitems}
	}
\end{cventries}
