%-------------------------------------------------------------------------------
%    SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications: Posters}


%-------------------------------------------------------------------------------
%    CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
	
	%---------------------------------------------------------
	\cventry
	{} % Affiliation/role
	{} % Organization/group
	{} % Location
	{} % Date(s)
	{
		\begin{cvitems} % Description(s) of experience/contributions/knowledge
			\item {Rasheed A, Tabib M,  \textbf{Siddiqui MS}, Kvamsdal T, Kvarving AM, Fuchs F, Okstad KM, “GONE with the WIND”, SINTEF Group Meet Dept. of Applied Mathematics, 8-9 May 2017, Oslo, Norway.}
			\item {Rasheed A, Tabib M,  \textbf{Siddiqui MS}, Fonn E, Kvamsdal T, Kvarving AM, Okstad KM, “Multiscale Wind Modelling”, SINTEF Group Meet Dept. of Applied Mathematics, 8-9 May 2017, Oslo, Norway.}
			\item {Fonn E, Rasheed A, Tabib M, Kvamsdal T,  \textbf{Siddiqui MS}, Kvarving AM, Okstad KM, “Torturing Data with Artificial Intelligence”, SINTEF Group Meet Dept. of Applied Mathematics, 8-9 May 2017, Oslo, Norway.}
			\item {Tabib M, Rasheed A, \textbf{Siddiqui MS}, “A 3D Vs 2.5D Vs 2D CFD analysis of 5MW NREL reference wind-turbine to study impact of bluff sections”,14th Deep Sea Offshore Wind R\&D Conference, Deepwind, 18-21 January 2017, Trondheim, Norway.}
			\item {\textbf{Siddiqui MS}, Rasheed A, Tabib M, Kvamsdal T, “Simulating Single turbine and associated wake development - validation and comparison of computational methods (Actuator Line Vs Sliding Mesh Interface Vs Multiple Reference Frame)”, 14th Deep Sea Offshore Wind R\&D Conference, Deepwind, 18-21 January 2017, Trondheim, Norway.}
			\item {\textbf{Siddiqui MS}, Rasheed A, Tabib M, Kvamsdal T, “Explaining the Torque vs. TSR  curve of a 5MW NREL reference turbine”,14th Deep Sea Offshore Wind R\&D Conference, Deepwind, 18-21 January 2017, Trondheim, Norway.}
			\item {\textbf{Siddiqui MS} “Fluid Surface Interaction (FSI) analysis of Mega Watt Size Offshore Wind Turbine”, Math Meets Industry Conference, 22-23 September Trondheim, Norway.}    
			\item {\textbf{Siddiqui MS}, Rasheed A, Tabib M, Kvamsdal T “Numerical Analysis of NREL 5MW Wind Turbine: A Study Towards a Better Understanding of Wake Characteristic and Torque Generation Mechanism ”, The Science of Making Torque from Wind Conference, Torque, 4-7 October, Munich, Germany.}            
			\item {\textbf{Siddiqui MS}, Rasheed A,  Kvamsdal T, Tabib M, “Three Dimensional Variable Turbulent Intensity Flow Field Characterization of a Vertical Axis Wind Turbine”, 12th Deep Sea Offshore Wind R\&D Conference, Deepwind, 4-6 February 2015, Trondheim, Norway.}                
		\end{cvitems}
	}
\end{cventries}
