\cvsection{Publications: Conferences}
\begin{cventries}
	\cventry
	{} % Affiliation/role
	{} % Organization/group
	{} % Location
	{} % Date(s)
	{
		\begin{cvitems} 
			\item{\textbf{Siddiqui MS}, Rasheed A, Kvamsdal T, Fonn E, 2018 “Wake Characterization of NREL 5MW using Proper Orthogonal Decomposition and Large Eddy Simulation”, AIAA Scitech Conference , 8-12 January, Kissimmee, Florida, USA.}
			\item{\textbf{Siddiqui MS}, Rasheed A, Tabib M, Kvamsdal T, 2017 “Numerical Modeling Framework for Wind Turbine Analysis \& Atmospheric Boundary Layer Interaction  ”, AIAA Scitech Conference , 9-13 January, Grapevine Texas, USA.}
			\item {\textbf{Siddiqui MS}, Rasheed A, Kvamsdal T, Tabib M, 2015 “Three Dimensional Variable Turbulent Intensity Flow Field Characterization of a Vertical Axis Wind Turbine”, 12 Deep Sea Offshore Wind R$\&$D Conference, Deepwind, 4-6 February, Trondheim, Norway.}
			\item {Ahmed F, Rahman S, \textbf{Siddiqui MS}, 2014 “Optimization of an Internal Combustion Engine`s Efficiency for Fuel Conservation and Green Environment” International Conference on Energy Systems and Policies, 24-27 November, Islamabad, Pakistan.}
			\item {\textbf{Siddiqui MS}, Hassan SM, 2014 “Optimized Design of a Straight Blade Urban Roof Top Vertical Axis Wind Turbine” International Conference on Energy Systems and Policies, 24-27 November, Islamabad, Pakistan.}
			\item{\textbf{Siddiqui MS}, Ahmad H, Shaheer M, 2014 “Numerical Simulation of a Compressed Air Driven Tesla Turbine” ASME Power Conference July 28-31, Baltimore, Maryland, USA.}
			\item{Rabbani T, Saif M, \textbf{Siddiqui MS}, Akhtar I, and Durrani N, 2014 “Reduced Order Modeling Of Loads On A Vertical-Axis Wind Turbine” Proceedings of International Bhurban Conference on Applied Sciences and Technology 15 – 18 January Islamabad, Pakistan}
			\item{Suleman K, Asim MS, Kamran M, \textbf{Siddiqui MS}, 2013 “Mathematical modeling of a single piston Gasoline Engine and Simulation of Efficiency Parameters” International Conference on Modeling and Simulation, 24-27 September, Islamabad, Pakistan}
			\item{\textbf{Siddiqui MS}, Durrani N, Akhtar I, 2013 “Numerical Study to Quantify the Effects of Struts and Central Hub on the Performance of A Three Dimensional Vertical Axis Wind Turbine Using Sliding Mesh” ASME Power Conference, July 26-31, Boston, Massachusetts, USA}
			\item{\textbf{Siddiqui MS}, Durrani N, Akhtar I, 2012 “Effect Of Third-Dimensionality On Vertical Axis Wind Turbine Blades: A Numerical Study” 2nd International Symposium on Frontiers of Computational Sciences 28-29 June, Islamabad, Pakistan.}
			\item{\textbf{Siddiqui MS}, Hassan SM, Kamran M, 2012 “Quick Return, flexible flap angle mechanism for a flapping wing Micro Air Vehicle” International Conference on Engineering Sciences, Institute of Chemical Engineering and Technology, February 28-29, Lahore, Pakistan.}
			\item{\textbf{Siddiqui MS}, Hassan SM, Kamran M, 2012 “Stress Analysis for Active Flapping and Pitching Mechanism of an Micro Air Vehicle” International Conference on Engineering Sciences, Institute of Chemical Engineering and Technology, February 28-29, Lahore, Pakistan.}
			\item{Kamran M, \textbf{Siddiqui MS}, Hassan SM, 2012 “Comparison among Conventional Blocks and Bricks with Compressed Stabilized Earth Blocks” International Conference on Engineering Sciences, Institute of Chemical Engineering and Technology, February 28-29, Lahore, Pakistan.}
			\item{Hassan SM, Nadeem M, \textbf{Siddiqui MS}, 2011 “An algorithm for the generation/selection of process plans based upon production rate” International Conference on Advance Modeling and Simulation, NUST College of EME, June 17-21, Rawalpindi, Pakistan.}    
		\end{cvitems}
	}
\end{cventries}