%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
% \geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%    PERSONAL INFORMATION
%    Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
\name{Sidra}{Latif}
\position{Fresh Graduate}
\address{Baldersveg 3B, Trondheim, Norway}

\mobile{(+47) 48628035} 
\email{sidra.latif@outlook.com}
\linkedin{sidraLatif}
% \stackoverflow{SOid}{SOname}
% \twitter{@twit}
% \skype{skypeid}
% \extrainfo{extra informations}

%-------------------------------------------------------------------------------
%    LETTER INFORMATION
%    All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
{HR Manager}
{EVRY}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Data Scientist}
% How the letter is opened
\letteropening{Dear Sir/Madem,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
%\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}
	
	% Print the header with above personal informations
	\makecvheader
	
	% Print the footer with 3 arguments(<left>, <center>, <right>)
	% Leave any of these blank if they are not needed
	\makecvfooter
	{\today}
	{M. Salman Siddiqui~~~·~~~Cover Letter}
	{}
	
	% Print the title with above letter informations
	\makelettertitle
	
	%-------------------------------------------------------------------------------
	%    LETTER CONTENT
	%-------------------------------------------------------------------------------
	\begin{cvletter}
		
		\lettersection{About Me}
		
		I am applying for the position available in the company that was recently advertised on the website under the title Data Scientist
		
		I am a fresh graduate and have recently received my Bachelors in Computer Sciences from International Islamic University Islamabad, Pakistan with a CGPA of $\textbf{3.96/4.0}$ in 2017. I moved to Trondheim Norway in January 2018. 
		\lettersection{Why Me?}
 I had the singular honor of receiving the Presidential Gold Medal for outstanding academic achievement in my undergraduate degree. I was awarded the maximum scholarship in all semesters during my undergraduate degree program.	My research paper titled \emph{A novel Cryptographic method developed towards the application of image processing} is under review in \emph{IEEE Symposium on Logic in Computer Science}, that will be held at Oxford UK in July 2018. In this paper, we proposed a novel method which will bring state of the art understanding of Cryptographic methods in the field of image processing field.  Ranging from poetry to sports, I have left hardly any stone unturned in this respect. I was a member of my college and high school badminton and chess teams. I was also the senior most Appointment holder, both at the high school as well as in university. As a volunteer, I joined the ERRA and helped the victims of 2005 Earthquake at Pakistan Institute of Medical Sciences.
 
 As an enthusiastic young woman, with my strong academic and professional background, currently I am embarking myself to learn the science behind Machine Leaning/Artificial Intelligence and Data Analytics through online courses on \emph{Coursera} (https://www.coursera.org/learn/machine-learning). I believe that continued acquisition of advanced knowledge will place me in a good stead for  multitude of career prospects. 

	  
\lettersection{Why NUMECA International Y?}
The good reputation of EVRY with higher employees standards, diverse cultural environment, and cutting edge research facilities have motivated me to apply for the current position. I believe this position will help me acquire versatility needed to reach my full potential as a professional researcher. I consider myself ready for the challenges of the current position, and I am sure that I will contribute very positively to your dynamic company.
	\end{cvletter}
	
	
	%-------------------------------------------------------------------------------
	% Print the signature and enclosures with above letter informations
	\makeletterclosing
	
\end{document}
