\cvsection{Publications: Journals}
\begin{cventries}
  \cventry
    {} % \textbf{Siddiqui MS}ffiliation/role
    {} % Organization/group
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems}
\item {Tabib M, Rasheed A, \textbf{Siddiqui MS} “Influence of Tip Speed Ratio on Wake Flow Characteristics Utilizing Fully Resolved CFD Methodology ”, Journal of Physics Conference Series (Wake Conference), pp. xxxx, 2017.}
\item {\textbf{Siddiqui MS}, Rasheed A,Tabib M, Kvamsdal T, “Influence of Tip Speed Ratio on Wake Flow Characteristics Utilizing Fully Resolved CFD Methodology ”, Journal of Physics Conference Series (Wake Conference), pp. xxxx, 2017.}
\item {\textbf{Siddiqui MS}, Rasheed A,Tabib M, Fonn E, Kvamsdal T, “On the interaction between Wind Farms and Marine Boundary Layer”, OMAE, pp. xxxx, 2017.}
\item {Rasheed A, Kvamsdal T, Tabib M, \textbf{Siddiqui MS}, “Wind Energy Modelling from 2D blade sections to Wind farms”, OMAE, pp. xxxx, 2017.}
\item {Tabib M, Rasheed A, Fonn E, \textbf{Siddiqui MS}, “Analysis of unsteady hydrodynamics relevant to vortex induced vibrations on bluff-bodied offshore structure”, OMAE, pp. xxxx, 2017.}
\item {\textbf{Siddiqui MS}, Rasheed A,Tabib M, Kvamsdal T, “Explaining the Torque vs TSR curve of a 5MW NREL reference turbine”, Elsevier Energy Procedia Journal, pp. xxxx, 2017.}
\item {\textbf{Siddiqui MS}, Rasheed A, Tabib M, Kvamsdal T, “Simulating Single turbine and associated wake development - validation and comparison of computational methods (Actuator Line Vs Sliding Mesh Interface Vs Multiple Reference Frame)”, Elsevier Energy Procedia Journal, pp. xxxx, 2017.}
\item {Rasheed A, Tabib M, \textbf{Siddiqui MS}, Foon E, Suld JK, Kvamsdal T, “A comprehensive multiscale numerical framework for wind energy modelling”, Elsevier Energy Procedia Journal, pp. xxxx, 2017.}
\item {Tabib M, Rasheed A, Fonn E, Fuchs FG, \textbf{Siddiqui MS}, “CFD data based spectral and mode decomposition analysis of unsteady aerodynamics relevant to vortex induced vibrations on wind-turbine structure”, Elsevier Energy Procedia Journal, pp. xxxx, 2017.}
\item {Tabib M, Rasheed A, \textbf{Siddiqui MS}, “A 3D Vs 2.5D Vs 2D CFD analysis of 5MW NREL reference wind-turbine to study impact of bluff sections”, Elsevier Energy Procedia Journal, pp. xxxx, 2017.}
\item {Fonn E, Rasheed A, Tabib M, \textbf{Siddiqui MS}, “A step towards a reduced order modelling of flow characterized by wakes using Proper Orthogonal Decomposition”, Elsevier Energy Procedia Journal, pp. xxxx, 2017.}
\item{\textbf{Siddiqui MS}, Rasheed A, Tabib M, Kvamsdal T, “Insights on aerodynamics of the industrial-scale NREL 5MW reference wind turbine through comparison of different numerical frame-works with variable levels of geometric approximations ”, Wind Energy, 2016.}
\item{\textbf{Siddiqui MS}, Rasheed A, Kvamsdal T, Tabib M, “Comparison of 2D and 3D RANS Based Simulations of NACA0015 Offshore Wind Turbine Blade  ”, Elsevier Journal of Applied Energy, 2016.}
\item{\textbf{Siddiqui MS}, Rasheed A, Tabib M, Kvamsdal T, “Numerical Analysis of NREL 5MW Wind Turbine: A Study Towards a Better Understanding of Wake Characteristic and Torque Generation Mechanism ”, Journal of Physics Conference Series 753(2016)032059.}
\item {\textbf{Siddiqui MS}, Rasheed A, Kvamsdal T, Tabib M, “Three Dimensional Variable Turbulent Intensity Flow Field Characterization of a Vertical Axis Wind Turbine”, Elsevier Energy Procedia Journal, pp. 312-320, 2015.}
\item {Saif M, Rabbani T, Akhtar T, Durrani N, \textbf{Siddiqui MS}, “Reduced-Order Modeling of Torque on a Vertical-Axis Wind Turbine at Varying Tip-Speed Ratios”, Journal of Computational and Nonlinear Dynamics, American Society of Mechanical Engineers, Volume 10, , pp. 041012, 2015.}
\item {\textbf{Siddiqui MS}, Durrani N, Akhtar I, “ Quantification of the Effects of Geometric Approximations on the Performance of a Vertical Axis Wind Turbine: A Numerical Approach”, Elsevier Renewable Energy Journal, Volume 74, , pp. 661-670, 2015.}
\end{cvitems}
    }
\end{cventries}
