%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
	%---------------------------------------------------------
	\cventry
	{Research Scientist, Sintef Applied Mathematics} % Job title
	{SINTEF ICT} % Organization
	{Trondheim, Norway} % Location
	{Feb. 2015 - To Present} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Blade design of 10MW offshore wind turbine using CFD.
			}
			\item {Research and Development of  CFD codes.}
			 \item{Numerical investigation of wakes from wind turbine.}
		\end{cvitems}
	}
	
	%---------------------------------------------------------
  \cventry
  {Doctoral Assistant, Department of Mathematical Sciences} % Job title
  {Norwegian univeristy of sciences \& technology} % Organization
  {Trondheim, Norway} % Location
  {Feb. 2015 - To Present} % Date(s)
  {
  	\begin{cvitems} % Description(s) of tasks/responsibilities
  		\item {Development of fluid structure modeling tools for wind turbines.}
  		\item {Wind energy forecasting and wind turbine micrositing.}
  		\item {Development and application of CFD tools for simulating flow around a rotating turbine.}
  		\item{Development and application of mesh generators for wind turbines.}
  		\item{Development and application of geometry modeling for wind turbines.}
  	\end{cvitems}
  }
  %---------------------------------------------------------
%---------------------------------------------------------
\cventry
{Lecturer, Mechanical Engineering Department} % Job title
{Air University} % Organization
{Islamabad, Pakistan} % Location
{Sep. 2012 - Jan. 2015} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Subjects taught: Engineering Drawing and Graphics, Engineering Dynamics, Thermodynamics, CAD/CAM/CAE.}
		\item {Supervised final year projects on Wind Turbines, Automated Screw Jacks, Heat Exchangers etc.}
		\item {Implemented and revised the curriclum of Thermo-Fluids as per the instructions of Pakistan Engineering Council(PEC).}
	\end{cvitems}
}

%---------------------------------------------------------


%---------------------------------------------------------

  \cventry
    {Junior Lecturer, Mechanical Engineering Department} % Job title
    {HITEC(Heavy Industry Taxila Education City)} % Organization
    {Taxila, Pakistan} % Location
    {Dec. 2010- Aug. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Laboratories taught: Engineering drawing and graphics, CAD/CAM(manual, autocad/autodesk and pro.engineer), mechanics of materials.} 
        \item {Advanced training on Creo Parametric from Trojans Pakistan.}
      \end{cvitems}
    }


%---------------------------------------------------------


%---------------------------------------------------------
\end{cventries}