%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications: Journals}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {} % Affiliation/role
    {} % Organization/group
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
\item{\underline{M. Salman}, A. Rasheed, M. Tabib, T.  Kvamsdal,  “Numerical Frame Work for NREL 5MW Wind Turbine using Variable Level of Geometric Approximations  ”, Wind Energy, June 2016.}
\item{\underline{M. Salman}, A. Rasheed, T.  Kvamsdal, M. Tabib, “Comparison of 2D and 3D RANS Based Simulations of NACA0015 Offshore Wind Turbine Blade  ”, Elsevier Journal of Applied Energy, January 2016.}
\item{M. Tabib, A. Rasheed, \underline{M. Salman} “A full-scale 3D Vs 2.5D Vs 2D analysis of flow-patterns and forces at different sections of 5MW NREL reference wind-turbine and its implications for strip-theory and blade element method based approach”, Elsevier Energy Procedia Journal, June 2016 (Submitted)} 
\item{\underline{M. Salman}, A. Rasheed, M. Tabib, T.  Kvamsdal, “Numerical Analysis of NREL 5MW Wind Turbine: A Study Towards a Better Understanding of Wake Characteristic and Torque Generation Mechanism  ”, Journal of Physics , October 2016.}
\item {\underline{M. Salman}, A. Rasheed, T.  Kvamsdal, M. Tabib, “Three Dimensional Variable Turbulent Intensity Flow Field Characterization of a Vertical Axis Wind Turbine”, Elsevier Energy Procedia Journal, November 2015, Pages. 312-320.}
\item {M. Saif, T. Rabbani, I. Akhtar, N.Durani, \underline{M. Salman}, “Reduced-Order Modeling of Torque on a Vertical-Axis Wind Turbine at Varying Tip-Speed Ratios” Journal of Computational and Nonlinear Dynamics, American Society of Mechanical Engineers, Volume 10, June 2015, Pages. 041012.}\item {\underline{M. Salman}, N.  Durrani, I. Akhtar, “ Quantification of the Effects of Geometric Approximations on the Performance of a Vertical Axis Wind Turbine: A Numerical Approach” Elsevier Renewable Energy Journal, Volume 74, February 2015, Pages. 661-670.}
      \end{cvitems}
    }


\end{cventries}
